### 2021-11-25 input/proposal.tex
minor

\begin{lemma}[\label{def:detection}\underline{D}etector existence (D)]
  Assuming a chain of delivery of $\alpha_x$ from \Process~$x$ to
  \Process~$z$ with $\alpha_x = \min D_z$, if $x$ broadcasts a
  staleness notification $\delta_x$, either $z$ eventually delivers
  it, or a \process of the delivery chain $[x,\ldots, z]$ eventually
  detects its blocking.
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}

\begin{proof}
  %% knowing that b_p delta is sufficient to say that processes will
  %% receive delta or detect blocking
  (A) Assuming a chain of delivery $C = [x, \ldots, z]$ of $\alpha_x$
  with $\forall p \in C: \alpha_x = \min D_p$, and assuming
  $d_x(\delta_x)$, then with forwarding of staleness
  (Definition~\ref{def:fs}), $f_{C[k]}(\delta_x) \implies \eventually
  d_{C[k+1]}(\delta_x)$ except if $\delta_x \in D_{C[k+1]}$ which
  means that $C[k+1]$ already delivered and forwarded $\delta_x$
  following another such a chain of delivery. Therefore, $z$
  eventually receives, hence delivers $\delta_x$.

  \noindent (B) Assuming a chain of delivery $C = [x, \ldots, z]$ of
  $\alpha_x$ with at least $\alpha_x = \min D_z$, and assuming
  $d_x(\delta_x)$, then by (A), the staleness notification reaches a
  \process $C[k]$. By Definition~\ref{def:fs}, the fowarding stops
  when $C[k]$ already delivered $\delta_x$ (covered by (A)) or
  delivered a better message $\alpha_x \neq \alpha_y = \min
  D_{C[k]}$. The latter means that $\eventually d_{C[k+1]}(\alpha_y)$
  or $\delta_y \in D_{C[k+1]}$.

  %% (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
  %% but whose parent is neither inconsistent (like $b$) nor receiving
  %% $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
  %% \process, either directly or transitively, for such a child \process
  %% ($d$) trusts the possible removal of $P_X$ by delivering and
  %% forwarding such $\Delta$. $\Delta$ suffers from identical blocking
  %% conditions (between $b$ and $c$) than $\delta$, leading to the same
  %% solutions of detection and propagation of $\Delta$. Eventually,
  %% every \process whose last delivery is $\alpha_X$ receives and
  %% delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
\end{proof}

>>>>

\begin{lemma}[\label{def:detection}$\textup{FB}^+ \wedge \textup{FS}
  \implies$ \underline{D}etector existence (D)]
  Assuming $\textup{FB}^+$, $\textup{FS}$, a chain of delivery on
  $\pi_{xz}$ of $\alpha_x$ with $\alpha_x = \min D_z$, if $x$
  broadcasts a staleness notification $\delta_x$, either $z$
  eventually delivers it, or a \process $y\in\pi_{xz}$ eventually
  detects its blocking.
  % $b_p(\delta_x) \implies d_q(x) U Detect[X]$ ??? 
\end{lemma}

\begin{proof}
  %% knowing that b_p delta is sufficient to say that processes will
  %% receive delta or detect blocking
  (A) Assuming a chain of delivery $\pi_{xz} = [x, \ldots, z]$ of
  $\alpha_x$ with $\forall y \in \pi_{xz}: \alpha_x = \min D_y$, and
  assuming $d_x(\delta_x)$, then with forwarding of staleness
  (Definition~\ref{def:fs}),
  $f_{\pi_{xz}[k]}(\delta_x) \implies \eventually
  d_{\pi_{xz}[k+1]}(\delta_x)$ except if $\delta_x \in D_{\pi_{xz}[k+1]}$ which
  means that $\pi_{xz}[k+1]$ already delivered and forwarded $\delta_x$
  following another such a chain of delivery. Therefore, $z$
  eventually receives, hence delivers $\delta_x$.

  \noindent (B) Assuming a chain of delivery
  $\pi_{xz} = [x, \ldots, z]$ of $\alpha_x$ with at least
  $\alpha_x = \min D_z$, and assuming $d_x(\delta_x)$, then by (A),
  the staleness notification reaches a \process $\pi_{xz}[k]$. By
  Definition~\ref{def:fs}, the fowarding stops when $\pi_{xz}[k]$
  already delivered $\delta_x$ (covered by (A)) or delivered a better
  message $\alpha_x \neq \alpha_y = \min D_{\pi_{xz}[k]}$. The latter
  means that $\eventually d_{\pi_{xz}[k+1]}(\alpha_y)$ or
  $\delta_y \in D_{\pi_{xz}[k+1]}$.
  %
  %% (i) If every \process (such as $a$) starting from the source
  %% delivers and forwards a removal notification $\delta_X$ when their
  %% last delivery is $\alpha_X$, then every such \process eventually
  %% delivers the removal notification $\delta_X$ except \processes (such
  %% as $b$) that delivered $\alpha_X$ from a \process that delivered a
  %% message from another partition $\alpha_Y$ since then.
  %
  %% These exceptions eventually receive and deliver $\alpha_Y$ since
  %% $\alpha_Y$ is better than $\alpha_X$ through this path, except if
  %% they already received and delivered the removal notification of
  %% $P_Y$ (such as $c$). These \processes may never receive hence
  %% deliver $\delta_X$, and may never receive hence deliver a better
  %% message than $\alpha_X$. They need an additional mechanism to
  %% eventually purge $\alpha_X$ that cannot rely on the eventual purging
  %% of $P_Y$ at \processes like $b$, to avoid deadlocks.
  %
  %% (ii) Assuming that every \process keeps an history of its past
  %% deliveries, \processes (such as $c$) can detect the inconsistency,
  %% since they receive from their parent an already deleted partition
  %% $P_Y$. This notification means that the parent discards any
  %% $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
  %% $\delta_X$ exists, it discards it. To ensure the purge of stale
  %% messages, a detecting \process must assume the worst case that such
  %% $\delta_X$ exists, and send another kind of message, noted $\Delta$,
  %% that notify the possible removal of $P_X$.
  %
  %% (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
  %% but whose parent is neither inconsistent (like $b$) nor receiving
  %% $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
  %% \process, either directly or transitively, for such a child \process
  %% ($d$) trusts the possible removal of $P_X$ by delivering and
  %% forwarding such $\Delta$. $\Delta$ suffers from identical blocking
  %% conditions (between $b$ and $c$) than $\delta$, leading to the same
  %% solutions of detection and propagation of $\Delta$. Eventually,
  %% every \process whose last delivery is $\alpha_X$ receives and
  %% delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
\end{proof}
